### 2014-03-12 src/methodology.Rnw
update

>>>>

For the first variant, we applied the x\% sampling to the result of the first
sampling based on line counts. That is, in the case of methods, we first
selected $#linecount$ mutants each from each method, and applied the x\%
selection to the result of this selection. For the second variant, we did
the sampling in one go, where we chose $#linecount/x$ number of mutants from
each program element.
